log

### 2020-03-30 manuscript/drafts/manuscript.tex

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={Manuscript drafts},
  pdfauthor={Gerbrich Ferdinands},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage[margin=1in]{geometry}
\usepackage{longtable,booktabs}
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}
\usepackage[]{biblatex}
\addbibresource{asreview.bib}

@@

A SR can be divided into phases. Everything starts with a
\textbf{systematic search}, leading to then citation screening is
performed, then full-text screening \autocite{PRISMA-PGroup2015}

@@

\autocite{modAL2018}

@@

\autocite{OMara-Eves2015} literature review

\autocite{Yu2018a}, \autocite{Yu2019} simulated 32 svm classifiers, on
software engineering. A popular classifier is SVM. succes with HUTM
(fastread), uncertainty, mix of weighting and agressive undersampling,
In terms of Yu et al, we adopt .CT.

SVM - tf-idf on medical data, uncertainty sampling, agressive
undersampling. \autocite{Wallace2010}

@@

SVM + Weighting + uncertainty (bow) produced good methods
\autocite{Miwa2014} Also include social sciences data besides medical
data.

\autocite{Cohen2006} perceptron-based classifier (neural network)

SVM on legal documents (no balancing, certainty ) \autocite{Cormack2014}
in limitations section mentions that LR yields about same results, nb
inferior results.

\autocite{Kilicoglu2009} - SVM, naive bayes, boosting and combinations.
future work should optimize parameters. ``Regarding the base classifiers
used in identifying method- ologically rigorous studies, boosting
consistently strikes the best balance between precision and recall,
whereas naive Bayes in general performs well on recall (demonstrating a
tradeoff between recall and precision), as does polynomial SVM on
precision. The AUC results are mixed, although boosting has a slight
edge overall. These results demonstrate that different classifiers can
be used to satisfy different information needs (SVM for specificity,
naive Bayes for sensitivity, and boosting for balance between the two,
for example).''

@@

Cohen et al.~collected systematic review datasets from the medical
sciences \autocite{Cohen2006}. All systematic reviews in this database
are on drug efficacy. The \emph{ace} dataset used in the current study
comes from a systematic review on the efficacy of Angiotensin-converting
enzyme (ACE) inhibitors.

a machine learning-based citation classification tool to reduce workload
in systematic reviews of drug class efficacy. Using a perceptron
classifier, \href{mailto:WSS@95}{\nolinkurl{WSS@95}}\% = 56.61 in
\autocite{Cohen2006}. (5x2 crossvalidation). Can we beat this? The data

The \emph{software} dataset is retrieved from \autocite{Yu2018a}, who
collected datasets on literature reviews from the software engineering
field. This dataset is on fault prediction in software engineering by
\autocite{Hall2012}.

The \emph{nudging} dataset comes from a review from the behavioural
public administration area. The SR includes studies on nudging
healthcare professionals \autocite{Nagtegaal2019}. The data was stored
on the Harvard Dataverse \autocite{Nagtegaal2019a}.

A literature review from field of psychology, \emph{ptsd}. The SR is on
studies applying latent trajectory analyses on posttraumatic stress
after exposure to trauma \autocite{vandeSchoot2017}. The corresponding
data can be found on the Open Science Framework {[}\ldots{]}.

\emph{wilson}, a dataset from the medical sciences
\autocite{Appenzeller-Herzog2020}. TA review on effectiveness treatments
of Wilson disease \autocite{Appenzeller-Herzog2019}.

@@

Naive Bayes (B) - predicts the class of an instance given input features
\(\mathbf{X}\). Naive Bayes assumes all features are independent given
the class value. This is obviously not the case but still the algorithm
performs impressively \autocite{Zhang2004}. Especially at \ldots{}
tasks.

Random Forests (R) is where a large number of decision trees are fit on
bootstrapped samples of the original data. All trees cast a vote on the
class, which are aggregated into a class prediciton for each input
\(\mathbf{X}\) \autocite{Breiman2001}.

Support Vecor Machine (S) - finds a multidimensional hyperplane to
separate classes. \autocite{Tong2001}

@@

A classical example is a `bag of words' representation. For each each
text, the number of occurrences of each word is stored. This leads to n
features, where n is the number of distinct words in the texts
\autocite{scikit-learn}. The bag-of-words method is simplistic and will
highly value often occuring but otherwise meaningless words such as
``and''. Term-frequency Inverse Document Frequency (TF-IDF)
\autocite{Ramos2003} circumvents this problem by adjusting a term
frequency in a text with the inverse docuement frequency, the frequency
of a given word in the entire corpus.

@@

Predicts words from context. Aims at capturing the relations between
word (man-woman, king-queen). \autocite{Le2014}. Using a neural network.

@@

From gensim \autocite{Rehurek2010}.

@@

BERT-base model with mean-tokens pooling \autocite{Reimers2019}

@@

Naive Bayes assumes all features are independent given the class value.
\autocite{Zhang2004}

ASReview uses the \texttt{MultinomialNB} from the scikit-learn package
\autocite{scikit-learn}, that implements the naive Bayes algorithm for
multinomially distributed data. \texttt{nb}

@@

A number of decision trees are fit on bootstrapped samples of the
original data, \autocite{Breiman2001} RandomForestClassifier from
sklearn

@@

\begin{itemize}
\tightlist
\item
  Max - Choose the most likely samples to be included according to the
  model
\item
  Uncertainty - choose the most uncertain samples according to the model
  (i.e.~closest to 0.5 probability) \autocite{Lewis1994}
\item
  Random - randomly selects abstracts with no regard to model assigned
  probabilities.
\item
  Cluster - Use clustering after feature extraction on the dataset. Then
  the highest probabilities within random clusters are sampled
\end{itemize}

@@

\printbibliography[title=References]

>>>>

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={Manuscript drafts},
  pdfauthor={Gerbrich Ferdinands},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage[margin=1in]{geometry}
\usepackage{longtable,booktabs}
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newenvironment{cslreferences}%
  {\setlength{\parindent}{0pt}%
  \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces}%
  {\par}

@@

A SR can be divided into phases. Everything starts with a
\textbf{systematic search}, leading to then citation screening is
performed, then full-text screening (PRISMA-P Group et al. 2015)

@@

(Danka and Horvath, n.d.)

@@

(O'Mara-Eves et al. 2015) literature review

(Yu, Kraft, and Menzies 2018), (Yu and Menzies 2019) simulated 32 svm
classifiers, on software engineering. A popular classifier is SVM.
succes with HUTM (fastread), uncertainty, mix of weighting and agressive
undersampling, In terms of Yu et al, we adopt .CT.

SVM - tf-idf on medical data, uncertainty sampling, agressive
undersampling. (Wallace et al. 2010)

@@

SVM + Weighting + uncertainty (bow) produced good methods (Miwa et al.
2014) Also include social sciences data besides medical data.

(Cohen et al. 2006) perceptron-based classifier (neural network)

SVM on legal documents (no balancing, certainty ) (Cormack and Grossman
2014) in limitations section mentions that LR yields about same results,
nb inferior results.

(Kilicoglu et al. 2009) - SVM, naive bayes, boosting and combinations.
future work should optimize parameters. ``Regarding the base classifiers
used in identifying method- ologically rigorous studies, boosting
consistently strikes the best balance between precision and recall,
whereas naive Bayes in general performs well on recall (demonstrating a
tradeoff between recall and precision), as does polynomial SVM on
precision. The AUC results are mixed, although boosting has a slight
edge overall. These results demonstrate that different classifiers can
be used to satisfy different information needs (SVM for specificity,
naive Bayes for sensitivity, and boosting for balance between the two,
for example).''

@@

Cohen et al.~collected systematic review datasets from the medical
sciences (Cohen et al. 2006). All systematic reviews in this database
are on drug efficacy. The \emph{ace} dataset used in the current study
comes from a systematic review on the efficacy of Angiotensin-converting
enzyme (ACE) inhibitors.

a machine learning-based citation classification tool to reduce workload
in systematic reviews of drug class efficacy. Using a perceptron
classifier, \href{mailto:WSS@95}{\nolinkurl{WSS@95}}\% = 56.61 in (Cohen
et al. 2006). (5x2 crossvalidation). Can we beat this? The data

The \emph{software} dataset is retrieved from (Yu, Kraft, and Menzies
2018), who collected datasets on literature reviews from the software
engineering field. This dataset is on fault prediction in software
engineering by (Hall et al. 2012).

The \emph{nudging} dataset comes from a review from the behavioural
public administration area. The SR includes studies on nudging
healthcare professionals (Nagtegaal et al. 2019a). The data was stored
on the Harvard Dataverse (Nagtegaal et al. 2019b).

A literature review from field of psychology, \emph{ptsd}. The SR is on
studies applying latent trajectory analyses on posttraumatic stress
after exposure to trauma (\noopsort{schoot}van de Schoot et al. 2017).
The corresponding data can be found on the Open Science Framework
{[}\ldots{]}.

\emph{wilson}, a dataset from the medical sciences (Appenzeller-Herzog
2020). TA review on effectiveness treatments of Wilson disease
(Appenzeller-Herzog et al. 2019).

@@

Naive Bayes (B) - predicts the class of an instance given input features
\(\mathbf{X}\). Naive Bayes assumes all features are independent given
the class value. This is obviously not the case but still the algorithm
performs impressively (Zhang 2004). Especially at \ldots{} tasks.

Random Forests (R) is where a large number of decision trees are fit on
bootstrapped samples of the original data. All trees cast a vote on the
class, which are aggregated into a class prediciton for each input
\(\mathbf{X}\) (Breiman 2001).

Support Vecor Machine (S) - finds a multidimensional hyperplane to
separate classes. (Tong and Koller 2001)

@@

A classical example is a `bag of words' representation. For each each
text, the number of occurrences of each word is stored. This leads to n
features, where n is the number of distinct words in the texts
(Pedregosa et al. 2011). The bag-of-words method is simplistic and will
highly value often occuring but otherwise meaningless words such as
``and''. Term-frequency Inverse Document Frequency (TF-IDF) (Ramos and
others 2003) circumvents this problem by adjusting a term frequency in a
text with the inverse docuement frequency, the frequency of a given word
in the entire corpus.

@@

Predicts words from context. Aims at capturing the relations between
word (man-woman, king-queen). (Le and Mikolov 2014). Using a neural
network.

@@

From gensim (Řehůřek and Sojka 2010).

@@

BERT-base model with mean-tokens pooling (Reimers and Gurevych 2019)

@@

Naive Bayes assumes all features are independent given the class value.
(Zhang 2004)

ASReview uses the \texttt{MultinomialNB} from the scikit-learn package
(Pedregosa et al. 2011), that implements the naive Bayes algorithm for
multinomially distributed data. \texttt{nb}

@@

A number of decision trees are fit on bootstrapped samples of the
original data, (Breiman 2001) RandomForestClassifier from sklearn

@@

\begin{itemize}
\tightlist
\item
  Max - Choose the most likely samples to be included according to the
  model
\item
  Uncertainty - choose the most uncertain samples according to the model
  (i.e.~closest to 0.5 probability) (Lewis and Catlett 1994)
\item
  Random - randomly selects abstracts with no regard to model assigned
  probabilities.
\item
  Cluster - Use clustering after feature extraction on the dataset. Then
  the highest probabilities within random clusters are sampled
\end{itemize}

@@

\hypertarget{references}{%
\section*{References}\label{references}}
\addcontentsline{toc}{section}{References}

\hypertarget{refs}{}
\begin{cslreferences}
\leavevmode\hypertarget{ref-Appenzeller-Herzog2020}{}%
Appenzeller-Herzog, Christian. 2020. ``Data from Comparative
Effectiveness of Common Therapies for Wilson Disease: A Systematic
Review and Meta-Analysis of Controlled Studies.'' Zenodo.

\leavevmode\hypertarget{ref-Appenzeller-Herzog2019}{}%
Appenzeller-Herzog, Christian, Tim Mathes, Marlies L. S. Heeres, Karl
Heinz Weiss, Roderick H. J. Houwen, and Hannah Ewald. 2019.
``Comparative Effectiveness of Common Therapies for Wilson Disease: A
Systematic Review and Meta-Analysis of Controlled Studies.'' \emph{Liver
International} 39 (11): 2136--52.
\url{https://doi.org/10.1111/liv.14179}.

\leavevmode\hypertarget{ref-Breiman2001}{}%
Breiman, Leo. 2001. ``Random Forests.'' \emph{Machine Learning} 45 (1):
5--32. \url{https://doi.org/10.1023/A:1010933404324}.

\leavevmode\hypertarget{ref-Cohen2006}{}%
Cohen, A. M., W. R. Hersh, K. Peterson, and Po-Yin Yen. 2006. ``Reducing
Workload in Systematic Review Preparation Using Automated Citation
Classification.'' \emph{Journal of the American Medical Informatics
Association : JAMIA} 13 (2): 206--19.
\url{https://doi.org/10.1197/jamia.M1929}.

\leavevmode\hypertarget{ref-Cormack2014}{}%
Cormack, Gordon V., and Maura R. Grossman. 2014. ``Evaluation of
Machine-Learning Protocols for Technology-Assisted Review in Electronic
Discovery.'' In \emph{Proceedings of the 37th International ACM SIGIR
Conference on Research \& Development in Information Retrieval},
153--62. SIGIR '14. Gold Coast, Queensland, Australia: Association for
Computing Machinery. \url{https://doi.org/10.1145/2600428.2609601}.

\leavevmode\hypertarget{ref-modAL2018}{}%
Danka, Tivadar, and Peter Horvath. n.d. ``modAL: A Modular Active
Learning Framework for Python.''

\leavevmode\hypertarget{ref-Hall2012}{}%
Hall, Tracy, Sarah Beecham, David Bowes, David Gray, and Steve Counsell.
2012. ``A Systematic Literature Review on Fault Prediction Performance
in Software Engineering.'' \emph{IEEE Transactions on Software
Engineering} 38 (6): 1276--1304.
\url{https://doi.org/10.1109/TSE.2011.103}.

\leavevmode\hypertarget{ref-Kilicoglu2009}{}%
Kilicoglu, H., D. Demner-Fushman, T. C. Rindflesch, N. L. Wilczynski,
and R. B. Haynes. 2009. ``Towards Automatic Recognition of
Scientifically Rigorous Clinical Research Evidence.'' \emph{Journal of
the American Medical Informatics Association} 16 (1): 25--31.
\url{https://doi.org/10/bjkhh9}.

\leavevmode\hypertarget{ref-Le2014}{}%
Le, Quoc V., and Tomas Mikolov. 2014. ``Distributed Representations of
Sentences and Documents.'' \emph{arXiv:1405.4053 {[}Cs{]}}, May.
\url{http://arxiv.org/abs/1405.4053}.

\leavevmode\hypertarget{ref-Lewis1994}{}%
Lewis, David D., and Jason Catlett. 1994. ``Heterogeneous Uncertainty
Sampling for Supervised Learning.'' In \emph{Machine Learning
Proceedings 1994}, edited by William W. Cohen and Haym Hirsh, 148--56.
San Francisco (CA): Morgan Kaufmann.
\url{https://doi.org/10.1016/B978-1-55860-335-6.50026-X}.

\leavevmode\hypertarget{ref-Miwa2014}{}%
Miwa, Makoto, James Thomas, Alison O'Mara-Eves, and Sophia Ananiadou.
2014. ``Reducing Systematic Review Workload Through Certainty-Based
Screening.'' \emph{Journal of Biomedical Informatics} 51 (October):
242--53. \url{https://doi.org/10.1016/j.jbi.2014.06.005}.

\leavevmode\hypertarget{ref-Nagtegaal2019}{}%
Nagtegaal, Rosanna, Lars Tummers, Mirko Noordegraaf, and Victor Bekkers.
2019a. ``Nudging Healthcare Professionals Towards Evidence-Based
Medicine: A Systematic Scoping Review.'' \emph{Journal of Behavioral
Public Administration} 2 (2).
\url{https://doi.org/doi.org/10.30636/jbpa.22.71}.

\leavevmode\hypertarget{ref-Nagtegaal2019a}{}%
---------. 2019b. ``Nudging Healthcare Professionals Towards
Evidence-Based Medicine: A Systematic Scoping Review.'' Harvard
Dataverse.

\leavevmode\hypertarget{ref-OMara-Eves2015}{}%
O'Mara-Eves, Alison, James Thomas, John McNaught, Makoto Miwa, and
Sophia Ananiadou. 2015. ``Using Text Mining for Study Identification in
Systematic Reviews: A Systematic Review of Current Approaches.''
\emph{Systematic Reviews} 4 (1): 5.
\url{https://doi.org/10.1186/2046-4053-4-5}.

\leavevmode\hypertarget{ref-scikit-learn}{}%
Pedregosa, F., G. Varoquaux, A. Gramfort, V. Michel, B. Thirion, O.
Grisel, M. Blondel, et al. 2011. ``Scikit-Learn: Machine Learning in
Python.'' \emph{Journal of Machine Learning Research} 12: 2825--30.

\leavevmode\hypertarget{ref-PRISMA-PGroup2015}{}%
PRISMA-P Group, David Moher, Larissa Shamseer, Mike Clarke, Davina
Ghersi, Alessandro Liberati, Mark Petticrew, Paul Shekelle, and Lesley A
Stewart. 2015. ``Preferred Reporting Items for Systematic Review and
Meta-Analysis Protocols (PRISMA-P) 2015 Statement.'' \emph{Systematic
Reviews} 4 (1): 1. \url{https://doi.org/10.1186/2046-4053-4-1}.

\leavevmode\hypertarget{ref-Ramos2003}{}%
Ramos, Juan, and others. 2003. ``Using Tf-Idf to Determine Word
Relevance in Document Queries.'' In \emph{Proceedings of the First
Instructional Conference on Machine Learning}, 242:133--42. Piscataway,
NJ.

\leavevmode\hypertarget{ref-Reimers2019}{}%
Reimers, Nils, and Iryna Gurevych. 2019. ``Sentence-BERT: Sentence
Embeddings Using Siamese BERT-Networks.'' \emph{arXiv:1908.10084
{[}Cs{]}}, August. \url{http://arxiv.org/abs/1908.10084}.

\leavevmode\hypertarget{ref-Rehurek2010}{}%
Řehůřek, Radim, and Petr Sojka. 2010. ``Software Framework for Topic
Modelling with Large Corpora.'' In \emph{Proceedings of the LREC 2010
Workshop on New Challenges for NLP Frameworks}, 45--50. Valletta, Malta:
ELRA.

\leavevmode\hypertarget{ref-Tong2001}{}%
Tong, Simon, and Daphne Koller. 2001. ``Support Vector Machine Active
Learning with Applications to Text Classification.'' \emph{Journal of
Machine Learning Research} 2 (Nov): 45--66.

\leavevmode\hypertarget{ref-vandeSchoot2017}{}%
\noopsort{schoot}van de Schoot, Rens, Marit Sijbrandij, Sonja D. Winter,
Sarah Depaoli, and Jeroen K. Vermunt. 2017. ``The GRoLTS-Checklist:
Guidelines for Reporting on Latent Trajectory Studies.''
\emph{Structural Equation Modeling: A Multidisciplinary Journal} 24 (3):
451--67. \url{https://doi.org/10/gdpcw9}.

\leavevmode\hypertarget{ref-Wallace2010}{}%
Wallace, Byron C., Thomas A. Trikalinos, Joseph Lau, Carla Brodley, and
Christopher H. Schmid. 2010. ``Semi-Automated Screening of Biomedical
Citations for Systematic Reviews.'' \emph{BMC Bioinformatics} 11 (1):
55. \url{https://doi.org/10.1186/1471-2105-11-55}.

\leavevmode\hypertarget{ref-Yu2018a}{}%
Yu, Zhe, Nicholas A. Kraft, and Tim Menzies. 2018. ``Finding Better
Active Learners for Faster Literature Reviews.'' \emph{Empirical
Software Engineering} 23 (6): 3161--86.
\url{https://doi.org/10.1007/s10664-017-9587-0}.

\leavevmode\hypertarget{ref-Yu2019}{}%
Yu, Zhe, and Tim Menzies. 2019. ``FAST2: An Intelligent Assistant for
Finding Relevant Papers.'' \emph{Expert Systems with Applications} 120
(April): 57--71. \url{https://doi.org/10.1016/j.eswa.2018.11.021}.

\leavevmode\hypertarget{ref-Zhang2004}{}%
Zhang, Harry. 2004. ``The Optimality of Naive Bayes.'' In
\emph{Proceedings of the Seventeenth International Florida Artificial
Intelligence Research Society Conference, FLAIRS 2004}. Vol. 2.
\end{cslreferences}

### 2020-03-30 simulation_study/README.Rmd

---
title: "logbook simulations"
output:   
  md_document:
    variant: markdown_github
---

@@

## Hyperparameter optimization
There are three stages, we start with the first where we are comparing different classifiers.

```{r include = FALSE}
library(tidyverse)
library(knitr)
library(kableExtra)
datasets <- c("ace", "nudging","ptsd",  "software", "wilson")
knitr::opts_chunk$set(echo = FALSE)
```

@@

# Stage 1 - Classifiers 
Comparing five different classifiers
```{r}
hyperparametersets <- readRDS("01_hyperparameter_sets.RDS")

# to-do grid 
todo <- hyperparametersets

# set emojis for grid 
check <- function(todo, m, ho, d){
  todo[todo$model %in% m & todo$hyperopt == ho, d] <- emo::ji("check") 
  return(todo)
}

busy <- function(todo, m, ho, d){
  todo[todo$model %in% m & todo$hyperopt == ho, d] <- emo::ji("timer") 
  return(todo)
}

huh <- function(todo, m, ho, d){
  todo[todo$model %in% m & todo$hyperopt == ho, d] <- emo::ji("question") 
  return(todo)
}

not <- function(todo, m, ho, d){
  todo[todo$model %in% m & todo$hyperopt == ho, d] <- emo::ji("x") 
  return(todo)
}

>>>>

---
title: "log"
output:   
  md_document:
    variant: markdown_github
---

@@

```{r include = FALSE}
library(tidyverse)
library(knitr)
library(kableExtra)
source("R/functions.R")
knitr::opts_chunk$set(echo = FALSE)
```

```{r eval = FALSE}
# 
source("R/00_condition_grid.R")
source("R/01_hyperparameter_sets.R")
```

## Hyperparameter optimization
There are three stages, we start with the first 5 where we are comparing different classifiers.

@@

# Stage 1 - Classifiers 
Comparing five different classifiers
```{r}
emptytodo <- readRDS("R/01_hyperparameter_sets.RDS")
